---
title: "104 project"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
1. t.test $conf.int
1.b z- calculate a,b 

nomal 1.qqnorm function 2.histgram 

3. compare budget, domestic gross and opening weekend for the following three categories
```{r}
data <- readxl::read_xlsx("hollywoodmovies.xlsx")

ind1 <- (data$Genre=="Horror")+0
ind2 <- (data$Genre=="Thriller")+0
ind_1 <- ind1+ind2

ind1 <- (data$Genre=="Animation")+0
ind2 <- (data$Genre=="Fantasy")+0
ind3 <- (data$Genre=="Romance")+0
ind_2 <- ind1+ind2+ind3

ind1 <- (data$Genre=="Action")+0
ind2 <- (data$Genre=="Animation")+0
ind_3<-ind1+ind2

group <- ind_1+2*ind_2+3*ind_3
data$group<-group
data1<-subset(data,data$group != 0)

aov1<-aov(data1$Budget~data1$group)
summary(aov1)

aov2<-aov(data1$DomesticGross~data1$group)
summary(aov2)

aov3<-aov(data1$OpeningWeekend~data1$group)
summary(aov3)


# nonparametric equivalents- Krustal Wallis
kruskal.test(Budget ~ group, data = data1)
kruskal.test(DomesticGross ~ group, data = data1)
kruskal.test(OpeningWeekend ~ group, data = data1)


```
The ANOVA test assumes that:
(1) The observations are obtained independently and randomly from the population defined by the factor levels
(2) The data of each factor level are normally distributed.
(3) These normal populations have a common variance.
The residuals versus fits plot can be used to check the homogeneity of variances.
```{r}
par(mfrow=c(3,2))
plot(aov1, c(1,2))
plot(aov2, c(1,2))
plot(aov3, c(1,2))

# Levene’s test to check the homogeneity of variances.
library(car)
leveneTest(Budget ~ factor(group), data = data)

# To check the normality more precisely, we did the Shapiro-Wilk test on the ANOVA residuals (W = 0.94268, p = 0.006) which finds that normality is violated.
# Extract the residuals
aov_residuals <- residuals(object = aov1 )
# Run Shapiro-Wilk test
shapiro.test(x = aov_residuals ) # normal
```





```{r}
# 4.
data2 <- subset(data,data$Genre=="Action")
cor(data2$DomesticGross, data2$OpeningWeekend, method = "pearson") #parametric
cor.test(data2$DomesticGross, data2$OpeningWeekend, method="pearson") #

cor(data2$DomesticGross, data2$OpeningWeekend, method = "spearman") #nonparametric
cor.test(data2$DomesticGross, data2$OpeningWeekend, method="spearman")

par(mfrow=c(1,2))
hist(data2$DomesticGross)
hist(data2$OpeningWeekend)
plot(data2$DomesticGross, data2$OpeningWeekend)

model_l<-lm(DomesticGross~Budget, data=data2)
summary(model_l)



# nonparametric one
library("lmPerm")
model_n<-lmp(DomesticGross~Budget, data=data2)
summary(model_n)

par(mfrow=c(1,2))
plot(model_l,c(1,2,3))
aov_residuals <- residuals(object = model_l )
# Run Shapiro-Wilk test
shapiro.test(x = aov_residuals )

```


5. paired test: paired t test
```{r}
data5<- subset(data,data$Genre=="Action")
# paired t test
t.test(data5$ForeignGross,data5$DomesticGross,paired = TRUE)

# non-parametric equivalent: Wilcoxon signed-rank test
wilcox.test(data5$ForeignGross,data5$DomesticGross,paired = TRUE)

# assumption
hist(data5$ForeignGross)
hist(data5$DomesticGross)
```

